Women in Kenya Severely Lack Knowledge on Source of Condom Supply Across All Age Groups And Provinces

### 2022-04-04 outputs/paper/paper.Rmd
modified some phrasing in paper.Rmd. Added content to README.md.

The raw dataset is parsed using the package `pdftools` [@citePDF]
and the statistical programming language R [@citeR] from 
Table 10.14.1 and Table 10.14.2 on page 170 and 171 of the PDF respectively 
[@citeDHS]. Two tables are parsed instead of one because the tables each present
data on only one gender. Therefore a dataset that combines data from both
genders in order to provide a more accurate analysis. As such,
a new variable, `gender`, is constructed to help distinguish the data between
female and male participants. Additionally, there is an issue in that the rows
of the tables corresponded to different variables; for example, some rows 
contained data for certain age groups while other rows contained data for 
different marital statuses. To simplify the analysis process, only the rows 
pertaining to age groups, education, and provinces were parsed from the PDF.

>>>>

The raw dataset is parsed using the package `pdftools` [@citePDF]
and the statistical programming language R [@citeR] from 
Table 10.14.1 and Table 10.14.2 on page 170 and 171 of the PDF respectively 
[@citeDHS]. Two tables are parsed instead of one because the tables each present
data on only one gender. Therefore a dataset that combines data from both
genders in order to provide a more accurate analysis. As such,
a new variable, `gender`, is constructed to help distinguish the data between
female and male participants. Additionally, there is an issue in that the rows
of the tables corresponded to background characteristics; for example, some rows 
contained data for certain age groups while other rows contained data for 
different marital statuses. To simplify the analysis process, only the rows 
pertaining to age groups, education, and provinces were parsed from the PDF
(Three datasets are constructed as a result instead of a single one).
